The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free e-learning program CrypTool\\ (10th edition -- distributed with CrypTool version 1.4.30)} \vspace{60pt}

### 2009-08-14 script/en/chapters/numbertheory.tex
typo
enable verbose in footnotes using \VerbatimFootnotes; fixed some TODOs

\noindent Below is Sage source code~\ref{nt_sagesample_Count_RSA_Keys} which can answer
this question concretely (if the modulus is not too big).   % TODO: Kann ich auf diesen Sourcecode verweisen? 
                           % TODO: Warum wird er nach Kap. 4.19 erst eingefügt?

@@

# DD_Start -- Testcases for count_Number_of_RSA_Keys(start, end)
print "\n\nDD_Start -- Testcases for count_Number_of_RSA_Keys(start, end)"

print "\n-----------Testcase: (100, 1000) [Should deliver 34.816]"
time count_Number_of_RSA_Keys(100, 1000)

print "\n-----------Testcase: (100, 107, True) [Should deliver 23]"
time count_Number_of_RSA_Keys(100, 107, True)

u = 10^3; o = 10^4;
print "\n-----------Testcase: (%s, " % u + "%s) [Should deliver 3.260.044]" % o
time count_Number_of_RSA_Keys(u, o)
# DD_End -- Testcases

@@

% TODO Joerg
% Warum ist das so?
% sage: count_Number_of_RSA_Keys(100, 100, True)
% Number of private keys for modulus in a given range: 0
% Number of primes in a given range: 0

% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\pagebreak
\newpage
\pagebreak
\hypertarget{NumberTheory_Appendix_F}{}  %\hypertarget{AppendixListAndDef}{}
\section{Appendix: List of the definitions and theorems formulated in this chapter}
\label{l:NumberTheory_Appendix_F}{}  %\label{l:AppendixListAndDef}{}

>>>>

\noindent Below is Sage source code~\ref{nt_sagesample_Count_RSA_Keys} which can answer
this question concretely (if the modulus is not too big).

@@

print "\n\nDD_Start -- Testcases for count_Number_of_RSA_Keys(start, end)"
print "\n-----------Testcase: (100, 1000) [Should deliver 34.816]"
time count_Number_of_RSA_Keys(100, 1000)
print "\n-----------Testcase: (100, 107, True) [Should deliver 23]"
time count_Number_of_RSA_Keys(100, 107, True)
u = 10^3; o = 10^4;
print "\n-----------Testcase: (%s, " % u + "%s) [Should deliver 3.260.044]" % o
time count_Number_of_RSA_Keys(u, o)

@@

% ++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++++
\newpage
\hypertarget{NumberTheory_Appendix_F}{}  %\hypertarget{AppendixListAndDef}{}
\section{Appendix: List of the definitions and theorems formulated in this chapter}
\label{l:NumberTheory_Appendix_F}{}  %\label{l:AppendixListAndDef}{}

### 2009-08-14 script/en/chapters/what-is-sage.tex
typo
enable verbose in footnotes using \VerbatimFootnotes; fixed some TODOs

From within a Sage session, we can obtain a list of commands matching
some pattern.  To do so, we type the first few characters and then
press the ``Tab'' key:
%
\begin{Verbatim}%
[fontsize=\footnotesize,fontshape=tt]
sage: Su[TAB]
Subsets                   Subwords                  SuzukiGroup
SubstitutionCryptosystem  SupersingularModule
\end{Verbatim}
%
If we know the exact name of a command, we can use the \texttt{help}
function to obtain further information on that command, or append the
question mark ``?'' to the command name.  For example,
the command \texttt{help(SubstitutionCryptosystem)} provides
documentation on the built-in class
\texttt{SubstitutionCryptosystem}. We can also obtain documentation on
this class as follows:
%
\begin{Verbatim}%
[fontsize=\footnotesize,fontshape=tt]
sage: SubstitutionCryptosystem?
Type:type
Base Class:<type 'type'>
String Form:<class 'sage.crypto.classical.SubstitutionCryptosystem'>
Namespace:Interactive
File:/home/mvngu/usr/bin/sage-3.4.1/local/lib/python2.5/site-packages/sage/crypto/classical.py
Docstring:

@@

At the beginning using a CAS (computer algebra system) you type in the single commands
on the command line as in the above example\footnote{%
  The standard way for presenting Sage code starts the lines with ``sage:'' and ``...''.
%  \begin{Verbatim}%       TODO Joerg (Paragraph ended before \FV@BeginScanning was complete.)
%  [fontsize=\footnotesize,fontshape=tt]
%  sage: m = 11
%  sage: for a in xrange(1, m):
%  ....:     print [power_mod(a, i, m) for i in xrange(1, m)]
%  ....:
%  \end{Verbatim}

>>>>

\noindent From within a Sage session, we can obtain a list of commands matching
some pattern.  To do so, we type the first few characters and then
press the ``Tab'' key:
%
\begin{Verbatim}%
[fontsize=\footnotesize,fontshape=tt]
sage: Su[TAB]
Subsets                   Subwords                  SuzukiGroup
SubstitutionCryptosystem  SupersingularModule
\end{Verbatim}
%
If we know the exact name of a command, we can use the \texttt{help}
function to obtain further information on that command, or append the
question mark ``?'' to the command name.  For example,
the command \texttt{help(SubstitutionCryptosystem)} provides
documentation on the built-in class
\texttt{SubstitutionCryptosystem}. We can also obtain documentation on
this class as follows:
%
\begin{Verbatim}%
[fontsize=\footnotesize,fontshape=tt]
sage: SubstitutionCryptosystem?
Type:type
Base Class:<type 'type'>
String Form:<class 'sage.crypto.classical.SubstitutionCryptosystem'>
Namespace:Interactive
File:/home/mvngu/usr/bin/sage-3.4.1/local/lib/python2.5/site-packages/sage/crypto/classical.py
Docstring:

@@

At the beginning using a CAS (computer algebra system) you type in the single commands
on the command line as in the above example\footnote{%
  The standard way for presenting Sage code starts the lines with ``sage:'' and ``...''.
  \begin{Verbatim}%
  [fontsize=\footnotesize,fontshape=tt]
  sage: m = 11
  sage: for a in xrange(1, m):
  ....:     print [power_mod(a, i, m) for i in xrange(1, m)]
  ....:
  \end{Verbatim}
